male code

### 2024-01-03 code/codeprocessmale.Rmd
adding code used for processing male data

---
title: "female code"
output: html_document
---

@@

#Calculate the mean and standard deviation of each United States female gymnast's score for each apparatus
usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w") %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Add a "Number of Observations" column to the usa_female_scores table
usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w") %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Num_Observations = n(),
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Create a table with the top 10 athletes with the highest mean scores for each apparatus and to plot each apparatus on separate graphs
  # Filter for USA female gymnasts
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w")

  # Group by apparatus, calculate mean, standard deviation, and number of observations
  usa_female_scores <- usa_female_scores %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Num_Observations = n(),
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
   )

  # Create a table with the top 10 athletes for each apparatus
  top_10_athletes <- usa_female_scores %>%
  group_by(Apparatus) %>%
  arrange(Apparatus, desc(Mean_Score)) %>%
  slice_head(n = 10)

  # Plot each apparatus on separate graphs
  for (apparatus in unique(top_10_athletes$Apparatus)) {
  data_subset <- filter(top_10_athletes, Apparatus == apparatus)
  p <- ggplot(data_subset, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
    geom_point() +
    geom_text(hjust = 0, vjust = 0) +
    labs(title = paste("Top 10 Female Athletes in", apparatus),
         x = "Standard Deviation", y = "Mean Score")
  print(p)
  }

@@

#Calculate the means and standard deviations for the specified US female athletes across all apparatuses
 # Filter for USA female athletes
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "w")

  # Define the list of last names
  target_last_names <- c("biles", "mcclain", "blakely", "sumanasekera", "jones", "carey", "chiles", "matthews", "wong", "lincoln", "dicello")

  # Filter the data for the specified athletes
  selected_athletes <- usa_female_scores %>%
  filter(LastName %in% target_last_names)

@@

#Calculate the sum of means and standard deviations for the targeted athletes from the athlete_apparatus_scores table
  # Define the list of last names
  target_last_names <- c("biles", "mcclain", "blakely", "sumanasekera", "jones", "carey", "chiles", "matthews", "wong", "lincoln", "dicello")

@@

#Create a scatter plot of the summed means on the y-axis and summed standard deviations on the x-axis
  # Create a scatter plot
  p <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
  geom_point() +
  geom_text(hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Female All-Around Candidates")

@@

  # Create a scatter plot for the top 10 combinations
  p <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Top 10 Combinations of 3 Female Athletes with Highest Mean Score")

@@

  # Create a scatter plot for the top 10 combinations
  p <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Top 10 Combinations of 4 Female Athletes with Highest Mean Score")

>>>>

---
title: "male code"
output: html_document
---

@@

#Calculate the mean and standard deviation of each male gymnast's score for each apparatus
male_scores <- data %>%
  filter(Gender == "m") %>%
  group_by(Apparatus, LastName, FirstName) %>%
  summarize(
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Calculate the mean and standard deviation of each United States male gymnast's score for each apparatus
usa_male_scores <- data %>%
  filter(Country == "USA" & Gender == "m") %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Add a "Number of Observations" column to the usa_male_scores table
usa_male_scores <- data %>%
  filter(Country == "USA" & Gender == "m") %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Num_Observations = n(),
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
  )

#Create a table with the top 10 athletes with the highest mean scores for each apparatus and to plot each apparatus on separate graphs
  # Filter for USA male gymnasts
  usa_female_scores <- data %>%
  filter(Country == "USA" & Gender == "m")

  # Group by apparatus, calculate mean, standard deviation, and number of observations
  usa_male_scores <- usa_male_scores %>%
  group_by(Apparatus, LastName) %>%
  summarize(
    Num_Observations = n(),
    Mean_Score = mean(Score),
    SD_Score = sd(Score)
   )

  # Create a table with the top 10 athletes for each apparatus
  top_10_athletes <- usa_male_scores %>%
  group_by(Apparatus) %>%
  arrange(Apparatus, desc(Mean_Score)) %>%
  slice_head(n = 10)

  # Plot each apparatus on separate graphs
  for (apparatus in unique(top_10_athletes$Apparatus)) {
  data_subset <- filter(top_10_athletes, Apparatus == apparatus)
  p <- ggplot(data_subset, aes(x = SD_Score, y = Mean_Score, label = LastName)) +
    geom_point() +
    geom_text(hjust = 0, vjust = 0) +
    labs(title = paste("Top 10 Male Athletes in", apparatus),
         x = "Standard Deviation", y = "Mean Score")
  print(p)
  }

@@

#Calculate the means and standard deviations for the specified US male athletes across all apparatuses
 # Filter for USA male athletes
  usa_male_scores <- data %>%
  filter(Country == "USA" & Gender == "m")

  # Define the list of last names
  target_last_names <- c("juda", "young", "moldauer", "hong", "hale", "malone", "whittenburg", "loos", "bock", "walker")

  # Filter the data for the specified athletes
  selected_athletes <- usa_male_scores %>%
  filter(LastName %in% target_last_names)

@@

#Calculate the sum of means and standard deviations for the targeted athletes from the athlete_apparatus_scores table
  # Define the list of last names
  target_last_names <- c("juda", "young", "moldauer", "hong", "hale", "malone", "whittenburg", "loos", "bock", "walker")

@@

#Create a scatter plot of the summed means on the y-axis and summed standard deviations on the x-axis
  # Create a scatter plot
  p <- ggplot(sums, aes(x = Sum_SD, y = Sum_Means, label = LastName)) +
  geom_point() +
  geom_text(hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Sum of Means", title = "Male All-Around Candidates")

@@

  # Create a scatter plot for the top 10 combinations
  p <- ggplot(top_10_combinations, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Top 10 Combinations of 3 Male Athletes with Highest Mean Score")

@@

  # Create a scatter plot for the top 10 combinations
  p <- ggplot(top_10_combinations_4, aes(x = SD_Sum, y = Mean_Score)) +
  geom_point() +
  geom_text(aes(label = Combination), hjust = 0, vjust = 0) +
  labs(x = "Sum of Standard Deviations", y = "Mean Score") +
  ggtitle("Top 10 Combinations of 4 Male Athletes with Highest Mean Score")
